---
title: East TN information
output:
  html_document:
    includes:
       in_header: GA_Script.html
params:
  sumtab: "unknown"
---

The purpose of this is to gather information on how the covid-19 pandemic is progressing in Medford, MA. It is **not** an official site; please go to https://www.medfordma.org/coronavirus-information/ for official information.

I am mostly doing this for the convenience of my family who live in Medford -- they wanted to see plots of things like positivity rate over time. 

Please keep my family, and yours, and yourself safe by following public health guidelines. Find a vaccine at https://vaxfinder.mass.gov/ and go [here](https://www.medfordma.org/coronavirus-information/) for info on boosters, masking, and more.


```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("_packages.R")
source("R/functions.R")
tar_load(medford_from_state)
tar_load(medford_from_city)
```

Positivity rates (what percent of tests show covid; if this is high, it could indicate that many other cases are being missed).

```{r, echo=FALSE, message=FALSE, warning=FALSE}	
plot_positivity <- ggplot(medford_from_state, aes(x=End_Date, y=Percent_Positivity)) + geom_line()+ theme_light() + xlab("Date") + ylab("Positivity rate of tests for the week ending this date")
print(plot_positivity)
```

New covid cases per day in Medford

```{r, echo=FALSE, message=FALSE, warning=FALSE}	
plot_cases <- ggplot(medford_from_city, aes(x=DATE, y=`New Cases`)) + geom_line()+ theme_light() + xlab("Date") + ylab("Number of new cases per day")
print(plot_cases)
```
