---
title: Medford MA covid information
output:
  html_document:
    includes:
       in_header: GA_Script.html
params:
  sumtab: "unknown"
---

The purpose of this is to gather information on how the covid-19 pandemic is progressing in Medford, MA. It is **not** an official site; please go to https://www.medfordma.org/coronavirus-information/ for official information.

I am mostly doing this for the convenience of my family who live in Medford -- they wanted to see plots of things like positivity rate over time. 

Please keep my family, and yours, and yourself safe by following public health guidelines. Find a vaccine at https://vaxfinder.mass.gov/ and go [here](https://www.medfordma.org/coronavirus-information/) for info on boosters, masking, and more.


```{r, echo=FALSE, message=FALSE, warning=FALSE}
source("_packages.R")
source("R/functions.R")
tar_load(medford_from_state)
#tar_load(medford_from_city)
tar_load(hhs_capacity_ma)
tar_load(hhs_capacity_ma_focal)
tar_load(hhs_capacity_ma_focal_latest_pretty)
tar_load(state_hospital_data)
```

Positivity rates (what percent of tests show covid; if this is high, it could indicate that many other cases are being missed).

```{r, echo=FALSE, message=FALSE, warning=FALSE}	
plot_positivity <- ggplot(medford_from_state, aes(x=End_Date, y=Percent_Positivity)) + geom_line()+ theme_light() + xlab("Date") + ylab("Percent of positive tests for the week ending this date") + ggtitle("Positivity rate in Medford")
print(plot_positivity)
```



### Hospital data


The US Department of Health and Human Services gives data on hospital usage. Here are data of ICU bed availability for hospitals in this area with at least 25 staffed ICU beds, using data from the week starting `r max(hhs_capacity_ma_focal$DATE)`.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
knitr::kable(hhs_capacity_ma_focal_latest_pretty)
```

The state also releases information about conditions in all hospitals in the state:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
covid_patients_plot <- ggplot(state_hospital_data, aes(x=Date, y=`Total number of COVID patients in hospital today`)) + geom_line() + theme_light() + ylab("Total covid patients") +  xlab("Date") + ggtitle("Total number of patients hospitalized for covid in MA")
print(covid_patients_plot)
```

Including the number of patients in the ICU for covid:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
covid_patients_ICU_plot <- ggplot(state_hospital_data, aes(x=Date, y=ICU)) + geom_line() + theme_light() + ylab("Total covid patients in ICU in MA") +  xlab("Date") + ggtitle("Total number of patients in the ICU for covid in MA")
print(covid_patients_ICU_plot)
```

And those intubated:

```{r, echo=FALSE, message=FALSE, warning=FALSE}
covid_patients_intubated_plot <- ggplot(state_hospital_data, aes(x=Date, y=Intubated)) + geom_line() + theme_light() + ylab("Total intubated covid patients in MA") +  xlab("Date") + ggtitle("Total number of patients intubated for covid in MA")
print(covid_patients_intubated_plot)
```

Plotting percentage of ICU patients with covid over time (up to the week starting `r max(hhs_capacity_ma_focal$DATE)`). Some hospitals have much more frequently updated data than others; some is fairly gappy. This just plots the hospitals that average at least 25 staffed *adult* ICU beds per week.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
major_hospitals <- subset(hhs_capacity_ma_focal, total_staffed_adult_icu_beds_7_day_avg>=25)
all_names <- table(major_hospitals$hospital_name)
good_names <- all_names[all_names>50]
major_hospitals <- major_hospitals[major_hospitals$hospital_name %in% names(good_names),]
try(hospital_plot <- ggplot(major_hospitals, aes(x=DATE, y=percentage_adult_hospital_inpatient_ICU_bed_occupied_of_all_inpatient_ICU_beds)) + geom_line(aes(colour=hospital_name)) + theme_light() + ylab("Percent of ICU patients witth covid") + xlab("Date") + ggtitle("Percent of ICU patients with covid at major Greater Boston hospitals") + facet_wrap(~ hospital_name, ncol=2) + guides(colour=FALSE) + ylim(c(50, 100)))
print(hospital_plot)
```
